---
title: Rps10, a molecular barcode with high sensitivity and specificity for oomycetes
output: html_document
---

```{r setup, include=FALSE}
source("style.R")
library(plotly)
library(readr)
library(metacoder)
library(purrr)
library(oomycetedbtools)
library(stringr)
```

**OomyceteDB** provides quality-controlled, aligned and annotated Oomycete *rps10* sequences.
*rps10* is a mitochondrial locus chosen as a molecular barcode suitable for metabarcoding or amplicon sequencing specific to the Oomycetes.
The curated database can be downloaded or queried using BLAST (for any release).
We invite all members of the oomycete community to contribute sequences for new Oomycete species.
We will include any new taxon with a GenBank accession you share with us.

The following interactive figure shows the taxa currently represented in the database. Click on a taxon to zoom in and click on the center to zoom out again.


<!-- <iframe class = "shiny_frame" src="http://oomy.cgrb.oregonstate.edu:3838/grunwald/OomyceteDB_dev/contents" frameBorder="0">
</iframe> -->


```{r fig.width=10, fig.height=10}
# Load last release
release_data_data <- get_release_data()
current_release_name <- release_data_data$csv_path[which.max(release_data_data$release_number)]
current_release_path <- file.path(find_release_dir(), current_release_name)
rps10_data <- readr::read_csv(current_release_path)
rps10_data <- rps10_data[! is.na(rps10_data$classification), ]
rps10_data <- rps10_data[, c("oodb_id", "classification")]

# Convert to taxmap
obj <- parse_tax_data(rps10_data, class_sep = ";", class_cols = "classification")
obj <- filter_taxa(obj, taxon_names == "Oomycota", subtaxa = TRUE)
obj <- filter_taxa(obj, n_supertaxa <= 4)

parents <- map_chr(supertaxa(obj, recursive = FALSE, value = 'taxon_names'), function(x) {
  if (length(x) == 0) {
    return('')
  } else {
    return(x)
  }
})
fig <- plot_ly(
  ids =  taxon_names(obj),
  labels = taxon_names(obj),
  parents = parents,
  hovertext = paste0(n_obs(obj, data = "tax_data"), ' sequences\n',
                     ifelse(is_leaf(obj), '', paste(n_leaves(obj), 'species'))),
  type = 'treemap',
  branchvalues = 'total'
) 
fig
```
