---
title: "Download or search the database"
output: html_document
---

```{r setup, include=FALSE}
source("style.R")
library(readr)
library(purrr)
library(oomycetedbtools)
library(tidyverse)
library(DT)
```

There are multiple releases of the database.
For each release, there is a CSV and a FASTA version of the database.
Usually, you should use the latest release, unless you are trying to reproduce a previous analysis.

## CSV format

The CSV format encodes a table with one row per sequence, with the following columns: 

* "oodb_id": This is the unique numeric ID specific to OomyceteDB.
* "name": The binomial species name of the organism with spaces replaced by underscores.
* "strain": The name of the strain/isolate if available. If the strain is not available, it is left empty.
* "genbank_id": The NCBI accession number for the sequence submitted to genbank. Note that the version number (the number at the end, after the period) is not included.
* "taxon_id": The NCBI taxonomy id. This can be looked up using the NCBI accession number.
* "classification": The taxonomic classification separated by semicolons. This classification is curated by us and is not the taxonomic classification from NCBI associated with the NCBI taxid.

## The FASTA header format

The FASTA formated file has headers with the same information as the CSV format in the following format:

```{r comment=NA}
release_data <- get_release_data()
current_fasta_name <- release_data$fasta_path[which.max(release_data$release_number)]
current_fasta_path <- file.path(find_release_dir(), current_fasta_name)
cat(read_lines(current_fasta_path, n_max = 1))
```


## Download

```{r}
release_data %>%
  arrange(desc(release_number)) %>%
  mutate(csv_path = paste0('<a href="', file.path(find_release_dir(), csv_path), '">', csv_path, '</a>'),
         fasta_path = paste0('<a href="', file.path(find_release_dir(), fasta_path), '">', fasta_path, '</a>')) %>%
  rename("Release" = release_number, "Date released" = release_date, "CSV download" = csv_path, "FASTA download" = fasta_path, "Release notes" = description) %>%
  datatable(escape = FALSE, rownames = FALSE)
```


## Browse the database

```{r}
current_release_name <- release_data$csv_path[which.max(release_data$release_number)]
current_release_path <- file.path(find_release_dir(), current_release_name)
rps10_data <- readr::read_csv(current_release_path)

rps10_data %>%
  select(oodb_id,  name, strain, genbank_id, taxon_id) %>%
  datatable()
```

